Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-11-30 manuscripts/manuscript.Rmd
revising text

```{r Figure_1, fig.cap="ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
ex_long <- gather(ex, variable, value, year, species)

@@

To illustrate this tradeoff, we use an example from fisheries
management. Fig1a shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT20XX].  Fig1b 
shows the catch quota (Total Allowable Catch or TAC, before being adjusted
for overages or underages in the catch of each country in the previous year)
for the stock as set by the relevant
management agency [@ICCAT20XX]. Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, which could contribute to
the observed quota stability. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

@@

<!-- NOTE perhaps comment on the deviation from constant escapement !-->

As the example in Figure 1 makes clear, management policies will rarely be
as responsive as this constant escapement policy assumes. In this paper,
we explore conditions under which this lack of responsiveness may be a
rational response on the part of managers. Specifically, we consider a
case where managers seek to balance the benefits in terms of increased
profits from fishing from more finely tracking recruitment variations
with the growing costs associated with adjusting policies quickly to do
so. The policy adjustment costs involved could reflect pure administrative
transaction costs or preferences held by fishermen, fish processing plants
or other stakeholders, for less variable quotas. In seeking to account
for these policy adjustment costs, we recognize that we do not know just
what functional form they should take and that it will require a lot of
empirical work to estimate that. Therefore, we scope three candidate
functional forms that represent different assumptions about how these
costs operate to determine whether the results we obtain are sensitive
to such differences.

@@

To simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the intrinsic rate of increase of
the fish population is 1 and the equilibrium biomass for the equivalent
deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed log-normally with 
log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.

Sensitivity analysis appears
in the supplement, along with complete R code to replicate and further 
vary the setup).

Taken together this objective function \eqref{eq:objective} and the state
equation \eqref{eq:state_equation} define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman's equation.
We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.

We solve this problem on a finite time horizon of $T =$ `r OptTime` using
value iteration [@Mangel1988; @Clark2000].

@@

$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.$$

@@

$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.$$

@@

$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,$$

@@

In addition in the Supplementary Material, we compare our results with 
more conventional fisheries economic formulation in which additional
costs are applied to the control variables themselves, as opposed to
adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. 
Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
the long-term average stock size or quota size that is optimal.

Choice of parameters 
--------------------

<!--NOTE ci notation is confusing because it does not usually refer to c0 or c4 -->

Each policy adjustment cost function is characterized in terms of
a cost coefficient $c_i$. However, $c_i$ takes different units for each
functional form. Therefore, if seeking to compare the relative effect of
each penalty function on optimal management, it is unclear what
parameter values should be used. To address this issue, we calibrate
choices of $c_i$ so that each has a comparable impact on the optimal net
present value of fishery, broadly following the example of @Bovenberg2008.

<!--NOTE Jake to confirm these are still relevant and needed. 
        We are using a less sophisticated normalization than was 
        once discussed and may or may not need the citations now. -->

Figure 2 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs. The $c_i$ values are given in Table 1.

@@

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients that
induce the same reduction in maximum expected NPV. For example, the
dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
unconstrained value when optimally managed. We focus our examination of the models on how the type and severity of policy adjustment costs affects the optimal management strategy.

<!-- is chosen such that the
optimal stock size in the analogous deterministic problem is 5% larger
than that corresponding to the maximum sustainable yield in biomass
($c_0=XXX$). -->

@@

When considering the first formulation of policy adjustment costs
(linear costs, $\Pi_1$), the first panel of Figure 3 shows a typical pattern, in which
the optimal policy tends to avoid small policy adjustments, resulting in
periods of constant policy followed by sudden bursts of adjustment.
This results in a relatively step-like policy pattern. In contrast, the
second formulation (quadratic costs, $\Pi_2$) disproportionately penalizes large policy
adjustments. The corresponding optimal policy tracks all of the changes
made by the cost-free policy, but with smaller magnitude. This results
in a smoother $h_t$ curve, one that undershoots the larger oscillations
seen in the cost-free optimum in favor of a policy that changes
incrementally each year. Finally, the optimal policy for the third,
'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
might expect, because the magnitude of the adjustment made is not
reflected in the resulting penalty.

The comparisons shown in Figure 3 are for one realization (i.e. a
particular sequence of random number draws representing environmental
variability) and are made for a particular magnitude of policy
adjustment costs equal to `r reduction *100`% of the maximum expected net present value 
in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
how optimal harvest levels and corresponding optimal stock sizes are
affected by the magnitude of the costs of policy adjustment. This time
we show summary statistics across 50 replicate sets of environmental
conditions. We show the impact of policy adjustment costs on the
variance of both harvests and stock sizes through time; on the
autocorrelation of harvests and stock sizes through time.

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}

@@

ggplot(filter(stats_df, variable != 'cross.correlation'), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ variable, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") +
  xlab("Penalty size (as fraction of NPV0)")

write.csv(stats_df, "components/data/figure4.csv")
```

For example, when small policy adjustments cost little but large
adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
might have expected (see also @Ludwig1980 for this particular case). As
cost penalties increase in severity (i.e., $c_i$ increases), the
variance in quotas through time decreases and the autocorrelation of
quotas through time increases. This smoothing of the harvest quotas
through time has knock-on effects for the corresponding optimal stock
sizes, which also become more autocorrelated as the scaling on policy
adjustment costs ($c_i$) is increased. The autocorrelation in stock
sizes here reflects the lag involved in a more modest increase in
harvests taking longer to eliminate the signal of strong recruitment
events, when compared to a more immediately responsive constant
escapement policy.

Interestingly, as suggested by the realization in Fig. 3, including a
fixed cost of policy adjustment increases the variation in harvests
through time. This is the opposite of a smoothing effect. Follow-on
consequences for the other statistics are not as clear in this case.

Finally, the case where policy adjustment costs scale linearly with the
size of the adjustment ($\Pi_1$) appear to be something of a
middle of the road strategy, in that increasing the severity of policy
adjustment costs (increasing $c_i$ has little effect on the variance or
autocorrelation of optimal harvest rates or stock sizes. To reveal the
particular impact of policy adjustment costs of this type requires a
more targeted summary statistic. Specifically, for each run we
calculated the frequency with which the optimal policy involved
maintaining a positive quota across multiple time steps unaltered. This
type of policy is arguably the most commonly observed behavior in TAC
management, but is one that is very rarely observed to be part of the
optimal management strategy in the basic model without policy adjustment
costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$.

@@

While still not common for the particular parameter combinations we examine,
we find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes: over the 100 replicates
time series the harvest policy is strictly positive and identical in consecutive intervals
only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
`r no_shifts[["L1"]] * 100`% with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
these costs ($c_i$) increases.

@@

```{r}
fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs (Pi[1]). (Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).")
```

```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}

@@

Next we examine the consequences either of ignoring policy adjustment
costs when they are present or assuming they are present when they are
not. To do so, it helps to break-down the different contributions to the
maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$
versus when employing the policy that would be optimal were there no
costs to policy adjustment $\bf{h_0}^*$. For example, if we take the
first of the adjustment penalty forms, $\Pi_1$

$$NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

and

$$NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

Histograms for the different contributions labelled $[1]-[4]$ here when
taken across 100 replicate runs are shown in Figure 5. Observe that the red
distributions (dockside profits) are relatively unchanged between policies based on the adjustment-free assumption (Reed, bottom row) vs when adjustments are properly accounted for (adjustment penalty, top row), while the blue distributions (costs for adjustment) are much larger in the bottom row then
in the top (when these costs have not been accounted for vs when they have
been taken into account.)  The cost of assuming policy adjustments are present when in fact they are
absent is given by subtracting the contribution to the first infinite
sum from term $[1]$ from the contribution to the second infinite sum of
term $[3]$. (Note that convergence properties
required to do this are met because we assume a positive discount rate).
This cost is positive because the optimal controls recommended when
assuming policy adjustment costs are present do not track variations in
stock size as closely. Therefore, this harvesting strategy provides
lower net revenue dockside.

In contrast, the cost of ignoring policy adjustment costs when in fact
they are present is given by subtracting the second infinite sum from
the first (contributions $([1]-[2])-([3]-[4]))$ in the equations. These
costs are positive because the lost revenues from not tracking stock
variations as closely are smaller than the penalties of policy
adjustment that are incurred if managers try to track stock variations
more tightly.

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7}

@@

Figure 6 compares these different contributions, namely the $NPV$ lost by
assuming policy adjustment costs when none are present (first entry in
each cell, $[3]-[1]$ in the equations)) and the $NPV$ lost when
ignoring policy adjustment costs when they are present (second entry in
each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the
equations) across the three different functional forms. Specifically,
the table shows how these values change as we vary the severity of
policy adjustment costs. In each case, values are shown as percentages
of the maximum expected $NPV$ in the base case where no policy
adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$.

We find a pronounced asymmetry when comparing the impact on the net
present value of the fishery of assuming policy adjustment costs are
present when they are absent with the impact of assuming they are absent
when they are present. For all three types of policy adjustment cost,
the impact on NPV of ignoring these costs if they are in fact present is
much bigger than that incurred by fallaciously managing as if they are
present when they do not occur. This asymmetry arises, because there is
less difference in the dockside revenue under the two management
recommendations than there is in the potential policy adjustment costs
themselves, as is evident in for the particular parameters shown in
Figure 5.

We also see that the impacts on net present value of the fishery of
incorrectly assuming or ignoring policy adjustment costs are most severe
when these costs are assumed to scale quadratically with the size of the
policy change being implemented ($\Pi_2$).

When policy costs are present, assuming the wrong functional form may or
may not be worse than ignoring the presence of policy costs all together.
Figure 7 considers several such cases.  The X axis labels indicate
first which policy is being used to drive the harvest decisions, and
then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
a policy calculated under the linear ($\Pi_1$) costs, when the reality
involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
costs have been scaled such that the net effect is the same, the inferred
policies differ.  As a result, the value is slightly more than half of
the optimal free solution when the expected reduction should only be 10% (panel A)
less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.

```{r Figure_7, fig.cap="Mismatches. X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty. Blue bars show the net present value of that scenario.  Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e. costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.  All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7}
who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
table2 <- arrange(mismatches_df[who], reduction) 
names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
table2_long$reduction <- as.factor(table2_long$reduction)

@@

<!-- Pasted from external word doc, see Boettiger_Discussion_draft.docx for latest version of discussion -->

@@

<!-- NOTE: Too many extensions being suggested now -->

@@

<!-- NOTE Paul writes: I can provide some references on this paragraph. But
would suggest that I wait and let you and others overhaul it first. I
am not sure it really adds much of value, but it does give us a
dismount. Moreover,  I'm trying to help you hit your desire to broaden
out beyond a fisheries context. The key barometer is we should be able
to point at a suitable sdp application which we could have used just as
easily as the fisheries management context. I think we can probably do
that for the list provided here.  -->

@@

Supplementary material
======================

## Economic penalties using quadratic costs

>>>>

```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).  Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1987 - 2007. Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
ex_long <- gather(ex, variable, value, stock, quota)

@@

To illustrate this tradeoff, we use an example from fisheries
management. Figure 1, top-left panel, shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT20XX].  The bottom-left panel 
shows the catch quota (Total Allowable Catch or TAC, before being adjusted
for overages or underages in the catch of each country in the previous year)
for the stock as set by the relevant
management agency [@ICCAT20XX]. Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, which could contribute to
the observed quota stability. Such patterns of variable stocks managed
under far less variable quotas are extremely common; for instance, 
in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the right-hand panels [@SEDAR2013]. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

@@

As the examples in Figure 1 make clear, management policies will rarely be
as responsive as this constant escapement policy assumes. In this paper,
we explore conditions under which this lack of responsiveness may be a
rational response on the part of managers. Specifically, we consider a
case where managers seek to balance the benefits in terms of increased
profits from fishing from more finely tracking recruitment variations
with the growing costs associated with adjusting policies quickly to do
so. The policy adjustment costs involved could reflect pure administrative
transaction costs or preferences held by fishermen, fish processing plants
or other stakeholders, for less variable quotas. In seeking to account
for these policy adjustment costs, we recognize that we do not know just
what functional form they should take and that it will require a lot of
empirical work to estimate that. Therefore, we scope three candidate
functional forms that represent different assumptions about how these
costs operate to determine whether the results we obtain are sensitive
to such differences.

@@

To simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the intrinsic rate of increase of
the fish population is 1 and the equilibrium biomass for the equivalent
deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed log-normally with 
log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.  
In the supplement we illustrate that the qualitative patterns observed
here are not sensitive to the specific choices for these parameter values.

Taken together this objective function \eqref{eq:objective} and the state
equation \eqref{eq:state_equation} define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman's equation.
We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.
We solve this problem on a finite time horizon of $T =$ `r OptTime` using
value iteration [@Mangel1988; @Clark2000].

Note that this problem is much larger computationally than the classic 
formulation of this stochastic dynamic programming problem for a single stock.
Whereas the classic problem considers each of $Q$ possible discrete quotas
for $S$ possible stock values at each time $t$, for a search space of size $S \times Q$
per timestep;  this formulation must also consider all possible values of quota
in the _previous_ time step: a total of $S \times Q \times Q$ configurations.

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper. Scripts for replicating 
all of the analysis presented here are also provided in the Supplementary Material.

<!-- Cite & link to Zenodo DOI here(?)-->

@@

\begin{equation}
\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.
\label{eq:Pi_1}
\end{equation}

@@

\begin{equation}
\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.
\label{eq:Pi_2}
\end{equation}

@@

\begin{equation}
\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,
\label{eq:Pi_3}
\end{equation}

@@

In the Supplementary Material, we compare our results with 
more conventional fisheries economic formulation in which additional
costs are applied to the control variables themselves, as opposed to
adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. 
Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
the long-term average stock size or quota size that is optimal.

<!-- State conclusion of this supplement here! -->

Comparing apples to apples
--------------------------

Before we can compare the policy dynamics resulting from each of these
functional froms, we must be careful to ensure that we are only varying
the _structure_ of the adjustment penalty and not the overall magnitude.
At the extremes, a large enough adjustment cost can ensure a constant 
policy, regardless of the structure; while a small enough one can be ignored
regardless.  Defining this calibration correctly is thus key to the entire
analysis.  Fortunately, the optimal control framework provides a completely
natural way to make this comparison: in terms of the _economic value_
(measured by $NPV$) of the stock in each case.  We will calibrate this relative
to economic value of the stock when adjustments to the policy are free ($NPV_0$).

Each policy adjustment cost function is characterized in terms of
a cost coefficient $c_i$. However, $c_i$ takes different units for each
functional form. Therefore, if seeking to compare the relative effect of
each penalty function on optimal management, it is unclear what
parameter values should be used. To address this issue, we calibrate
choices of $c_i$ so that each has a comparable impact on the optimal NPV
fishery.

Figure 2 shows the calibration graphically. Each curve plots the change
in maximum expected $NPV$ for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs. The $c_i$ values are given in Table 1.

@@

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients that
induce the same reduction in maximum expected NPV. For example, the
dashed vertical lines in Figure 2 map the needed cost coefficient $c_i$,
for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
unconstrained value when optimally managed. We focus our examination of the models on how
the type and severity of policy adjustment costs affects the optimal management strategy.

@@

The first panel shows a typical pattern resulting from linear adjustment costs ($\Pi_1$).
The optimal policy tends to avoid very small policy adjustments, resulting in
periods of a constant policy followed by sudden bursts of adjustment.
This results in a relatively step-like policy pattern. In contrast, the
second formulation (quadratic costs, $\Pi_2$) disproportionately penalizes large policy
adjustments. The corresponding optimal policy is typified by the middle panel, responding
to each of the fluctuations in stock, made by the cost-free policy, but with smaller 
magnitude response than the equivalent cost-free optimal solution. This results
in a smoother $h_t$ curve, one that undershoots the larger oscillations
seen in the cost-free optimum in favor of a policy that changes
incrementally each year. Finally, the optimal policy for the third,
'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
might expect, because the magnitude of the adjustment made is not
reflected in the resulting penalty.

These patterns are consistent across stochastic replicates over a range
of penalty magnitudes. The comparisons shown in Figure 3 are for one 
realization (i.e. a particular sequence of random number draws representing
environmental variability) and are made for one particular magnitude of 
policy adjustment costs (Calibrated to equal to `r reduction *100`% of the 
maximum expected net present valuein the base case ($NPV_0({\bf h_0^*})$,
as discussed in Figure 2, permitting comparisons between different forms).
To demonstrate this, we solved for the optimal policy under each of the
three adjustment cost scenarios for `r length(c0)` different penalty 
coefficients. For each resulting policy, we then simulated 50 stochastic
replicates of the stock dynamics managed under that policy.  To summarize
the patterns shown in Figure 3 and characterize the impact of increasingly
large fraction of the economic value (NPV) being consumed by policy
adjustment costs, we examine the response of several summary statistics
to increasing adjustment penalties (as a fraction of the adjustment-free value)
in Figure 4.  We show the impact of policy adjustment costs on the
variance & autocorrelation of the harvests through time.

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}

@@

f4df <- filter(figure4_df, timeseries=='harvest')
ggplot(f4df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") +
  xlab("Penalty size (as fraction of NPV0)")

write.csv(f4df, "components/data/figure4.csv")
```

Despite summarizing across such a large ensemble, Figure 4 confirms the
patterns we observed in the individual realizations shown in Figure 3.
For example, when small policy adjustments cost little but large
adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
might have expected (see also @Ludwig1980 for this particular case). As
cost penalties increase in severity (moving right along the horizontal axis,
larger fractions of the economic value are consumed by adjustment costs), the
variance in quotas through time decreases and the autocorrelation of
quotas through time increases. 
When adjustment costs are zero, all policies are slightly negatively autocorrelated:
this reflects the fact that a high harvest year is usually followed by a low harvest year
that allows the stocks to recover. However, as adjustment costs increase, the quadratic
policy tends to undershoot when stocks jump to very high or low levels, adjusting to compensate
over multiple years, as seen in Figure 3.  As a result, autocorrelation increases.

Interestingly, as suggested by the realization in Fig. 3, including a
fixed cost ($\Pi_1$) of policy adjustment increases the variation in harvests
through time. This is the opposite of a smoothing effect.

Finally, the case where policy adjustment costs scale linearly with the
size of the adjustment ($\Pi_1$) appear to be something of a
middle of the road strategy, in that increasing the severity of policy
adjustment costs. To reveal the
particular impact of policy adjustment costs of this type requires a
more targeted summary statistic. Specifically, for each run we
calculated the frequency with which the optimal policy involved
maintaining a positive quota across multiple time steps unaltered. This
type of policy is arguably the most commonly observed behavior in TAC
management, but is one that is very rarely observed to be part of the
optimal management strategy in the basic model without policy adjustment
costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$.

@@

While still not common for the particular parameter combinations we examine,
We find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes: over the 100 replicates
time series the harvest policy is strictly positive and identical in consecutive intervals
only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
`r no_shifts[["L1"]] * 100`% with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
these costs ($c_i$) increases.

@@

```{r}
fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs ($\Pi_1$). (Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).")
```

```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}

@@

Next we examine the consequences either of ignoring policy adjustment
costs when they are present or assuming they are present when they are
not. To do so, we run two kinds of simulations:

1. Simulations in which the optimal policy accounts for adjustment costs, 
   and those costs are present (in the form assumed),
2. Simulations in which the optimal policy _does not_ account for adjustment costs,

While the optimization guarentees that on average, the policy in the first simulation
should outperform that of the second, it does not tell us by how much.  These simulations
thus give us a lense to examine the magnitude of this effect.

We provide 100 replicates of each kind for each of the three forms
$\Pi_{1-3}$ (in which each ensemble of 100 replicates uses the same sequence of random seeds).
For each, we record (a) the dockside profits derived from fishing as well
as (b) any fees paid to make adjustments to the policy.  In the first kind of 
simulation, dockyard profits are almost less than in the second for a given stochastic
replicate, since the latter optimizes the expected dockside NPV.  However, the costs
paid for adjustment are almost always less in the first scenario as well, since
this solution explicitly tries to avoid higher adjustment costs.  We visualize this
pattern in the distributions shown in Figure 5 (focusing on $\Pi_1$ for simplicity,
as the pattern in $\Pi_2$ and $\Pi_3$ is similar, see Supplementary Material.)

Figure 5 shows that the difference in dockside revenue (labelled "profits" in the figure) 
between these two scenarios 
(green vs purple distributions) is very small, while a larger difference exists between
the costs paid for making policy adjustments (red vs blue). This is predicted by the optimization: 
the first scenario must outperform (or at least equal) the NPV of the second scenario
in aggregate, and as it cannot do so through higher profits it must do so through lower
costs.  Interestingly, for this set of parameters very little is lost in dockside revenue.
This suggests that the impact of assuming costs are present when they are not is rather small:
since the dockside revenue is none-the-less near optimal.  This also suggests that the 
converse error: ignoring costs when they are present, is more severe.

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

@@

We visualize the differences between these two errors directly in Figure 6. Subtracting revenue from
adjustment costs and considering only the mean across the replicates, we can dervive the expected $NPV$ 
in each case.  To standardize against a common baseline, we will express this value as a fraction of 
the cost-free optimum, $NPV_0$. Note that we have calibrated the optimal solutions to anticipate that
`r reduction*100`% of their $NPV$ would go into adjustment costs. When these adjustment costs are not 
actually present (blue bars, Fig 6), we thus expect a $NPV$ higher than the anticipated `r (1 -reduction)*100`%
but not quite as high as the optimal policy for that scenario (100%).  When adjustment costs are present
but the policy assumes that they are not (red bars), we would expect the $NPV$ to be less than `r (1 - reduction) * 100`%
of $NPV_0$ (since that's as good as the optimal solution for this scenario can do).

Figure 6 shows that across each penalty form $\Pi{1-3}$, the economic impact
of ignoring adjustment costs when they are present is higher than accounting
for them when they are absent. This holds even after accounting for effect 
described above: the red bars are consistently well below (`r (1-reduction)`),
while the blue bars are barely below 1.
We also see that the impacts on net present value of the fishery of
incorrectly assuming or ignoring policy adjustment costs are most severe
when these costs are assumed to scale quadratically with the size of the
policy change being implemented ($\Pi_2$).
In the Supplementary Materials we show that pattern holds across different
severity of adjustment costs (robust to choice of $c_i$), though the larger
the adjustment cost, the greater the difference between these two errors.

Note that this analysis does not consider the possibility that an adjustment cost
is present, but of a different functional form than the policy assumes.  Not surprisingly,
the consequences of managing under the wrong functional form can be as or more severe than
simply ignoring adjustment costs in the optimization all-together.  We illustrate several
of these mismatch errors in the Supplementary Material.

@@

@@

<!-- Comment on increasing variance or increasing autocorrelation from changes in policy costs / optimal management-->

@@

@@

# Supplementary material #

##  Impact on the stock dynamics ##

```{r StockDynamics, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

dt_s <- dt %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, fishstock, alternate, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)
